### 2016-06-16 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Updated instrumentation dimensions in channel list
Added test matrix to hose stream report; fixed channel list spacing in gas burner report

\subsection{Construction}
\label{sec:construction}
Each test structure was built on a concrete slab as shown in Fig.~\ref{fig:struct_pics}. The East Structure was designed to simulate a single-story residential structure, and the West Structure was designed to simulate a two-story residential structure. The first floor of each structure had an outer wall composed of interlocking concrete blocks with equal side lengths of 0.61~m (2~ft). The joints and gaps between the blocks were filled with high temperature insulation.

@@

The second floor of the West Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell. The second story walls were of wood-frame with 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers. The interior walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) durarock board, and a second layer of 16~mm (0.63~in) fire rated gypsum board. The exterior walls were protected with 11~mm (0.44~in) oriented strand board and 8~mm (0.31~in) fiber cement lap siding.

\subsection{Layout}
\label{sec:layout}
Dimensioned floor plans of the East and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.

@@

The ceiling height of each structure was approximately 2.4~m (8~ft). The interior dimensions of the East Structure were approximately 6.1~m (20~ft) by 11~m (36~ft), and the interior dimensions of the first and second floors of the West Structure were 5.8~m (19~ft) by 10.7~m (35.1~ft) and 6.1~m (20~ft) by 10.9~m (35.8~ft), respectively. The stairs connecting the two floors of the West Structure started 1.6~m (5.3~ft) off the interior south wall with a width of 1.2~m (4~ft) off the interior east wall and contained a 184~mm (7.25~in) rise and 191~mm (7.5~in) run. The exterior doors of both structures, the stairwell door on the second level of the West Structure, and the square roof vent in the East Structure with a 1.2~m (4~ft) side length and 320~mm (12.75~in) depth were opened and closed at certain instances during experiments to change the ventilation patterns within the structures. 
\FloatBarrier

@@

Three propane burners, pictured in Fig.~\ref{fig:burners}, were used as the fuel source in each experiment. Each burner had a square opening of side length 0.6~m (2~ft) located 0.14~m (5.5~in) above the floor and were positioned 0.6~m (2~ft) from the south and west walls on the first floor of each structure. Propane was supplied to the burners during all experiments. The flow of propane to each burner was controlled by a high-precision turn valve, and the total displaced gas volume was measured using a rotary gas meter.
% INCLUDE HRR CALCULATIONS HERE

@@

% MEASUREMENT TYPE FOR BDPs = 'Velocity' OR 'Pressure'?

@@

 & TC\_A7\_1  & 0.03~m below soffit  & Temperature \\
 & TC\_A7\_2  & 0.30~m below soffit  & Temperature \\

@@

 & TC\_A7\_4  & 0.91~m below soffit  & Temperature \\
 & TC\_A7\_5  & 1.22~m below soffit  & Temperature \\
 & TC\_A7\_6  & 1.52~m below soffit  & Temperature \\
 & TC\_A7\_7  & 1.83~m below soffit  & Temperature \\
 & TC\_A7\_8  & 2.13~m below soffit  & Temperature \\

@@

 & BDP\_A7\_1 & 0.03~m below soffit  & Velocity \\
 & BDP\_A7\_2 & 0.30~m below soffit  & Velocity \\

@@

 & BDP\_A7\_4 & 0.91~m below soffit  & Velocity \\
 & BDP\_A7\_5 & 1.22~m below soffit  & Velocity \\
 & BDP\_A7\_6 & 1.52~m below soffit  & Velocity \\
 & BDP\_A7\_7 & 1.83~m below soffit  & Velocity \\
 & BDP\_A7\_8 & 2.13~m below soffit  & Velocity \\

@@

 & TC\_A8\_1  & 0.03~m below soffit  & Temperature \\
 & TC\_A8\_2  & 0.30~m below soffit  & Temperature \\

@@

 & TC\_A8\_4  & 0.91~m below soffit  & Temperature \\
 & TC\_A8\_5  & 1.22~m below soffit  & Temperature \\
 & TC\_A8\_6  & 1.52~m below soffit  & Temperature \\
 & TC\_A8\_7  & 1.83~m below soffit  & Temperature \\
 & TC\_A8\_8  & 2.13~m below soffit  & Temperature \\

@@

 & BDP\_A8\_1 & 0.03~m below soffit  & Velocity \\
 & BDP\_A8\_2 & 0.30~m below soffit  & Velocity \\

@@

 & BDP\_A8\_4 & 0.91~m below soffit  & Velocity \\
 & BDP\_A8\_5 & 1.22~m below soffit  & Velocity \\
 & BDP\_A8\_6 & 1.52~m below soffit  & Velocity \\
 & BDP\_A8\_7 & 1.83~m below soffit  & Velocity \\
 & BDP\_A8\_8 & 2.13~m below soffit  & Velocity \\

@@

 & TC\_A9\_1  & 0.03~m below soffit  & Temperature \\
 & TC\_A9\_2  & 0.30~m below soffit  & Temperature \\

@@

 & TC\_A9\_4  & 0.91~m below soffit  & Temperature \\
 & TC\_A9\_5  & 1.22~m below soffit  & Temperature \\
 & TC\_A9\_6  & 1.52~m below soffit  & Temperature \\
 & TC\_A9\_7  & 1.83~m below soffit  & Temperature \\
 & TC\_A9\_8  & 2.13~m below soffit  & Temperature \\

@@

 & BDP\_A9\_1 & 0.03~m below soffit  & Velocity \\
 & BDP\_A9\_2 & 0.30~m below soffit  & Velocity \\

@@

 & BDP\_A9\_4 & 0.91~m below soffit  & Velocity \\
 & BDP\_A9\_5 & 1.22~m below soffit  & Velocity \\
 & BDP\_A9\_6 & 1.52~m below soffit  & Velocity \\
 & BDP\_A9\_7 & 1.83~m below soffit  & Velocity \\
 & BDP\_A9\_8 & 2.13~m below soffit  & Velocity \\

@@

Every thermocouple array contained eight bare-bead thermocouples, each bi-directional probe and solid thermocouple array contained 8 probes, and gas concentrations were pulled through 9.5~mm (0.38~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor. Each pair of total heat flux sensors were located 1.0~m (3.3~ft) above the floor. The pair at A16 contained one sensor facing the ceiling and another facing the north side of the room, and the pair at A17 also contained one sensor facing the ceiling and another facing the stairway door. The height of each individual sensor in the sensor arrays are listed in the channel list found in Table~\ref{table:west_channel_list}.
% \clearpage

@@

 & TC\_A5\_1  & 0.03~m below soffit  & Temperature \\
 & TC\_A5\_2  & 0.30~m below soffit  & Temperature \\

@@

 & TC\_A5\_4  & 0.91~m below soffit  & Temperature \\
 & TC\_A5\_5  & 1.22~m below soffit  & Temperature \\
 & TC\_A5\_6  & 1.52~m below soffit  & Temperature \\
 & TC\_A5\_7  & 1.83~m below soffit  & Temperature \\
 & TC\_A5\_8  & 2.13~m below soffit  & Temperature \\

@@

 & BDP\_A5\_1 & 0.03~m below soffit  & Velocity \\
 & BDP\_A5\_2 & 0.30~m below soffit  & Velocity \\

@@

 & BDP\_A5\_4 & 0.91~m below soffit  & Velocity \\
 & BDP\_A5\_5 & 1.22~m below soffit  & Velocity \\
 & BDP\_A5\_6 & 1.52~m below soffit  & Velocity \\
 & BDP\_A5\_7 & 1.83~m below soffit  & Velocity \\
 & BDP\_A5\_8 & 2.13~m below soffit  & Velocity \\

@@

 & TC\_A6\_1  & 0.03~m below soffit  & Temperature \\
 & TC\_A6\_2  & 0.30~m below soffit  & Temperature \\

@@

 & TC\_A6\_4  & 0.91~m below soffit  & Temperature \\
 & TC\_A6\_5  & 1.22~m below soffit  & Temperature \\
 & TC\_A6\_6  & 1.52~m below soffit  & Temperature \\
 & TC\_A6\_7  & 1.83~m below soffit  & Temperature \\
 & TC\_A6\_8  & 2.13~m below soffit  & Temperature \\

@@

 & BDP\_A6\_1 & 0.03~m below soffit  & Velocity \\
 & BDP\_A6\_2 & 0.30~m below soffit  & Velocity \\

@@

 & BDP\_A6\_4 & 0.91~m below soffit  & Velocity \\
 & BDP\_A6\_5 & 1.22~m below soffit  & Velocity \\
 & BDP\_A6\_6 & 1.52~m below soffit  & Velocity \\
 & BDP\_A6\_7 & 1.83~m below soffit  & Velocity \\
 & BDP\_A6\_8 & 2.13~m below soffit  & Velocity \\

@@

 & TC\_A10\_1  & 0.03~m below soffit & Temperature \\
 & TC\_A10\_2  & 0.30~m below soffit & Temperature \\

@@

 & TC\_A10\_4  & 0.91~m below soffit & Temperature \\
 & TC\_A10\_5  & 1.22~m below soffit & Temperature \\
 & TC\_A10\_6  & 1.52~m below soffit & Temperature \\
 & TC\_A10\_7  & 1.83~m below soffit & Temperature \\
 & TC\_A10\_8  & 2.13~m below soffit & Temperature \\

@@

 & BDP\_A10\_1 & 0.03~m below soffit  & Velocity \\
 & BDP\_A10\_2 & 0.30~m below soffit  & Velocity \\

@@

 & BDP\_A10\_4 & 0.91~m below soffit  & Velocity \\
 & BDP\_A10\_5 & 1.22~m below soffit  & Velocity \\
 & BDP\_A10\_6 & 1.52~m below soffit  & Velocity \\
 & BDP\_A10\_7 & 1.83~m below soffit  & Velocity \\
 & BDP\_A10\_8 & 2.13~m below soffit  & Velocity \\

@@

 & TC\_A11\_1  & 0.03~m below soffit  & Temperature \\
 & TC\_A11\_2  & 0.30~m below soffit  & Temperature \\

@@

 & TC\_A11\_4  & 0.91~m below soffit  & Temperature \\
 & TC\_A11\_5  & 1.22~m below soffit  & Temperature \\
 & TC\_A11\_6  & 1.52~m below soffit  & Temperature \\
 & TC\_A11\_7  & 1.83~m below soffit  & Temperature \\
 & TC\_A11\_8  & 2.13~m below soffit  & Temperature \\

@@

 & BDP\_A11\_1 & 0.03~m below soffit  & Velocity \\
 & BDP\_A11\_2 & 0.30~m below soffit  & Velocity \\

@@

 & BDP\_A11\_4 & 0.91~m below soffit  & Velocity \\
 & BDP\_A11\_5 & 1.22~m below soffit  & Velocity \\
 & BDP\_A11\_6 & 1.52~m below soffit  & Velocity \\
 & BDP\_A11\_7 & 1.83~m below soffit  & Velocity \\
 & BDP\_A11\_8 & 2.13~m below soffit  & Velocity \\

@@

 & TC\_A13\_1  & 0.03~m below soffit  & Temperature \\
 & TC\_A13\_2  & 0.30~m below soffit  & Temperature \\

@@

 & TC\_A13\_4  & 0.91~m below soffit  & Temperature \\
 & TC\_A13\_5  & 1.22~m below soffit  & Temperature \\
 & TC\_A13\_6  & 1.52~m below soffit  & Temperature \\
 & TC\_A13\_7  & 1.83~m below soffit  & Temperature \\
 & TC\_A13\_8  & 2.13~m below soffit  & Temperature \\

@@

 & BDP\_A13\_1 & 0.03~m below soffit  & Velocity \\
 & BDP\_A13\_2 & 0.30~m below soffit  & Velocity \\

@@

 & BDP\_A13\_4 & 0.91~m below soffit  & Velocity \\
 & BDP\_A13\_5 & 1.22~m below soffit  & Velocity \\
 & BDP\_A13\_6 & 1.52~m below soffit  & Velocity \\
 & BDP\_A13\_7 & 1.83~m below soffit  & Velocity \\
 & BDP\_A13\_8 & 2.13~m below soffit  & Velocity \\

@@

 & TC\_A14\_1  & 0.03~m below soffit  & Temperature \\
 & TC\_A14\_2  & 0.30~m below soffit  & Temperature \\

@@

 & TC\_A14\_4  & 0.91~m below soffit  & Temperature \\
 & TC\_A14\_5  & 1.22~m below soffit  & Temperature \\
 & TC\_A14\_6  & 1.52~m below soffit  & Temperature \\
 & TC\_A14\_7  & 1.83~m below soffit  & Temperature \\
 & TC\_A14\_8  & 2.13~m below soffit  & Temperature \\

@@

 & BDP\_A14\_1 & 0.03~m below soffit  & Velocity \\
 & BDP\_A14\_2 & 0.30~m below soffit  & Velocity \\

@@

 & BDP\_A14\_4 & 0.91~m below soffit  & Velocity \\
 & BDP\_A14\_5 & 1.22~m below soffit  & Velocity \\
 & BDP\_A14\_6 & 1.52~m below soffit  & Velocity \\
 & BDP\_A14\_7 & 1.83~m below soffit  & Velocity \\
 & BDP\_A14\_8 & 2.13~m below soffit  & Velocity \\

@@

 & HF\_2\_H	  & \begin{tabular}{l} 1~m above floor, \\ facing doorway (horizontal) \end{tabular} & Total heat flux \\
 & HF\_2\_V   & \begin{tabular}{l} 1~m above floor, \\ facing ceiling (vertical) \end{tabular} 	   & Total heat flux \\

@@

 & HF\_1\_H	  & \begin{tabular}{l} 1~m above floor, \\ facing doorway (horizontal) \end{tabular} & Total heat flux \\
 & HF\_1\_V	  & \begin{tabular}{l} 1~m above floor, \\ facing ceiling (vertical) \end{tabular} 	   & Total heat flux \\

@@

\section{East Structure Tests}
\label{sec:east_procedure}
Five different tests, Tests 2--6, were conducted in the East Structure. Table~\ref{table:HRR_East} lists the heat release rates for each experiment. The time between the ignition of each gas burner for Tests~2--4 was on the order of minutes, while the time between the ignition of each gas burner for Tests~5 and 6 was on the order of seconds. Thus, for Tests~2--4, heat release rates are reported for each time period between a burner being turned on or off, and a single heat release rate for when all burners were ignited is reported for Tests~5 and 6.

Tests~2--4 followed an identical order of events. Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for each test. A 61~cm (24~in) diameter PPV fan located 1.6~m (5.2~ft) away from the south exterior door was aimed at the center of the doorway and used during Tests~2--4. During these experiments, the south exterior door was not able to completely close due to an obstruction caused by the hoses used to transport propane to the burners. So, when the south door was in the ``closed'' position, a 133~mm (5.25~in) opening was present between the door and its frame. For all other experiments, however, the south exterior door was not used and the doorway remained closed for the entirety of the test. To fully close the doorway during these tests, the hinged door was removed and gypsum board was used to cover the doorway.

The procedures for Test~5 and Test~6 are outlined in Fig.~\ref{fig:east_test_5} and Fig.~\ref{fig:east_test_6}, respectively. Tests~5 and 6 involved repeating a specific set of events three times in a row. To avoid listing the identical actions three separate times in the event column of the table, each repetition of events has been denoted as a ``sequence'' (abbreviated as ``seq.'' in the tables) and given its own column in the event table.

\begin{table}[!ht]
\caption{Heat Release Rates for East Structure Tests}
\begin{tabular}{lccccc}
 \toprule
 					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
\textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
 \midrule
Test 2 				& 340 & 650	& 900 & 630 & 330 \\
Test 3 				& 330 & 650	& 910 & 630 & 330 \\
Test 4				& 350 & 650	& 950 & 650 & 340 \\
\midrule
 & \multicolumn{2}{c}{\textbf{Heat Release Rate (kW)}} & \multicolumn{3}{c}{} \\
\textbf{Test} 		& \multicolumn{2}{c}{All Burners On} 
& \multicolumn{3}{c}{} \\
\midrule
Test 5 - Seq. 1		& \multicolumn{2}{c}{730} & \multicolumn{3}{c}{} \\
Test 5 - Seq. 2		& \multicolumn{2}{c}{730} & \multicolumn{3}{c}{} \\
Test 5 - Seq. 3		& \multicolumn{2}{c}{720} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 1		& \multicolumn{2}{c}{720} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 2		& \multicolumn{2}{c}{720} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 3		& \multicolumn{2}{c}{710} & \multicolumn{3}{c}{} \\
\bottomrule
\end{tabular}
\label{table:HRR_East}
\end{table}

>>>>

\subsection{Construction}
\label{sec:construction}
Each test structure was built on a concrete slab as shown in Fig.~\ref{fig:struct_pics}. The East Structure was designed to simulate a single-story residential structure, and the West Structure was designed to simulate a two-story residential structure.

\subsubsection{First Floor of Both Structures}
The first floor of each structure had an outer wall composed of interlocking concrete blocks with equal side lengths of 0.61~m (2~ft). The joints and gaps between the blocks were filled with high temperature insulation.

@@

\subsubsection{Second Floor of West Structure}
The second floor of the West Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell. The second story walls were of wood-frame with 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers. The interior walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) durarock board, and a second layer of 16~mm (0.63~in) fire rated gypsum board. The exterior walls were protected with 11~mm (0.44~in) oriented strand board and 8~mm (0.31~in) fiber cement lap siding.

\subsection{Layout}
\label{sec:layout}

\subsubsection{Dimensions}
Dimensioned floor plans of the East and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.

@@

The ceiling height of each structure was approximately 2.4~m (8~ft). The interior dimensions of the East Structure were approximately 6.1~m (20~ft) by 11~m (36~ft), and the interior dimensions of the first and second floors of the West Structure were 5.8~m (19~ft) by 10.7~m (35.1~ft) and 6.1~m (20~ft) by 10.9~m (35.8~ft), respectively. The stairs connecting the two floors of the West Structure started 1.6~m (5.3~ft) off the interior south wall with a width of 1.2~m (4~ft) off the interior east wall and contained a 184~mm (7.25~in) rise and 191~mm (7.5~in) run. The exterior doors of both structures, the stairwell door on the second level of the West Structure, and the square roof vent in the East Structure with a 1.2~m (4~ft) side length and 320~mm (12.75~in) depth were opened and closed at certain instances during experiments to change the ventilation patterns within the structures. The exterior doors were made of steel, and the stairwell door on the second level of the West Structure was made of lauan plywood. 
% The roof vent was composed of 16~mm (0.63~in) thick Type X gypsum board (interior side) attached to

\subsubsection{Leakage}
An air leakage measurement system was used to measure the amount of leakage associated with each structure. The amount of leakage in the East Structure was measured as 0.024~m$^2$. For the West Structure, the leakage was measured as 0.027~m$^2$ when the stairway door was closed and as 0.054~m$^2$ when the stairway door was opened.

@@

Three propane burners, pictured in Fig.~\ref{fig:burners}, were used as the fuel source in each experiment. Each burner had a square opening of side length 0.6~m (2~ft) located 0.14~m (5.5~in) above the floor and were positioned 0.6~m (2~ft) from the south and west walls on the first floor of each structure. Propane was supplied to the burners during all experiments. The flow of propane to each burner was controlled by a high-precision turn valve, and the total displaced gas volume was measured using a rotary gas meter.

@@

@@

 & TC\_A7\_1  & 0.08~m below soffit  & Temperature \\
 & TC\_A7\_2  & 0.34~m below soffit  & Temperature \\

@@

 & TC\_A7\_4  & 0.88~m below soffit  & Temperature \\
 & TC\_A7\_5  & 1.15~m below soffit  & Temperature \\
 & TC\_A7\_6  & 1.42~m below soffit  & Temperature \\
 & TC\_A7\_7  & 1.68~m below soffit  & Temperature \\
 & TC\_A7\_8  & 1.95~m below soffit  & Temperature \\

@@

 & BDP\_A7\_1 & 0.08~m below soffit  & Velocity \\
 & BDP\_A7\_2 & 0.34~m below soffit  & Velocity \\

@@

 & BDP\_A7\_4 & 0.88~m below soffit  & Velocity \\
 & BDP\_A7\_5 & 1.15~m below soffit  & Velocity \\
 & BDP\_A7\_6 & 1.42~m below soffit  & Velocity \\
 & BDP\_A7\_7 & 1.68~m below soffit  & Velocity \\
 & BDP\_A7\_8 & 1.95~m below soffit  & Velocity \\

@@

 & TC\_A8\_1  & 0.08~m below soffit  & Temperature \\
 & TC\_A8\_2  & 0.34~m below soffit  & Temperature \\

@@

 & TC\_A8\_4  & 0.88~m below soffit  & Temperature \\
 & TC\_A8\_5  & 1.15~m below soffit  & Temperature \\
 & TC\_A8\_6  & 1.42~m below soffit  & Temperature \\
 & TC\_A8\_7  & 1.68~m below soffit  & Temperature \\
 & TC\_A8\_8  & 1.95~m below soffit  & Temperature \\

@@

 & BDP\_A8\_1 & 0.08~m below soffit  & Velocity \\
 & BDP\_A8\_2 & 0.34~m below soffit  & Velocity \\

@@

 & BDP\_A8\_4 & 0.88~m below soffit  & Velocity \\
 & BDP\_A8\_5 & 1.15~m below soffit  & Velocity \\
 & BDP\_A8\_6 & 1.42~m below soffit  & Velocity \\
 & BDP\_A8\_7 & 1.68~m below soffit  & Velocity \\
 & BDP\_A8\_8 & 1.95~m below soffit  & Velocity \\

@@

 & TC\_A9\_1  & 0.08~m below soffit  & Temperature \\
 & TC\_A9\_2  & 0.34~m below soffit  & Temperature \\

@@

 & TC\_A9\_4  & 0.88~m below soffit  & Temperature \\
 & TC\_A9\_5  & 1.15~m below soffit  & Temperature \\
 & TC\_A9\_6  & 1.42~m below soffit  & Temperature \\
 & TC\_A9\_7  & 1.68~m below soffit  & Temperature \\
 & TC\_A9\_8  & 1.95~m below soffit  & Temperature \\

@@

 & BDP\_A9\_1 & 0.08~m below soffit  & Velocity \\
 & BDP\_A9\_2 & 0.34~m below soffit  & Velocity \\

@@

 & BDP\_A9\_4 & 0.88~m below soffit  & Velocity \\
 & BDP\_A9\_5 & 1.15~m below soffit  & Velocity \\
 & BDP\_A9\_6 & 1.42~m below soffit  & Velocity \\
 & BDP\_A9\_7 & 1.68~m below soffit  & Velocity \\
 & BDP\_A9\_8 & 1.95~m below soffit  & Velocity \\

@@

Every thermocouple array contained eight bare-bead thermocouples, each bi-directional probe and solid thermocouple array contained 8 probes, and gas concentrations were pulled through 9.5~mm (0.38~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor. Each pair of total heat flux sensors were located 1.0~m (3.3~ft) above the floor. The pair at A16 contained one sensor facing the ceiling and another facing the north side of the room, and the pair at A17 also contained one sensor facing the ceiling and another facing the stairway door. The height of each individual sensor in the sensor arrays are listed in the channel list found in Table~\ref{table:west_channel_list}.

@@

 & TC\_A5\_1  & 0.08~m below soffit  & Temperature \\
 & TC\_A5\_2  & 0.34~m below soffit  & Temperature \\

@@

 & TC\_A5\_4  & 0.88~m below soffit  & Temperature \\
 & TC\_A5\_5  & 1.15~m below soffit  & Temperature \\
 & TC\_A5\_6  & 1.42~m below soffit  & Temperature \\
 & TC\_A5\_7  & 1.68~m below soffit  & Temperature \\
 & TC\_A5\_8  & 1.95~m below soffit  & Temperature \\

@@

 & BDP\_A5\_1 & 0.08~m below soffit  & Velocity \\
 & BDP\_A5\_2 & 0.34~m below soffit  & Velocity \\

@@

 & BDP\_A5\_4 & 0.88~m below soffit  & Velocity \\
 & BDP\_A5\_5 & 1.15~m below soffit  & Velocity \\
 & BDP\_A5\_6 & 1.42~m below soffit  & Velocity \\
 & BDP\_A5\_7 & 1.68~m below soffit  & Velocity \\
 & BDP\_A5\_8 & 1.95~m below soffit  & Velocity \\

@@

 & TC\_A6\_1  & 0.08~m below soffit  & Temperature \\
 & TC\_A6\_2  & 0.34~m below soffit  & Temperature \\

@@

 & TC\_A6\_4  & 0.88~m below soffit  & Temperature \\
 & TC\_A6\_5  & 1.15~m below soffit  & Temperature \\
 & TC\_A6\_6  & 1.42~m below soffit  & Temperature \\
 & TC\_A6\_7  & 1.68~m below soffit  & Temperature \\
 & TC\_A6\_8  & 1.95~m below soffit  & Temperature \\

@@

 & BDP\_A6\_1 & 0.08~m below soffit  & Velocity \\
 & BDP\_A6\_2 & 0.34~m below soffit  & Velocity \\

@@

 & BDP\_A6\_4 & 0.88~m below soffit  & Velocity \\
 & BDP\_A6\_5 & 1.15~m below soffit  & Velocity \\
 & BDP\_A6\_6 & 1.42~m below soffit  & Velocity \\
 & BDP\_A6\_7 & 1.68~m below soffit  & Velocity \\
 & BDP\_A6\_8 & 1.95~m below soffit  & Velocity \\

@@

 & TC\_A10\_1  & 0.08~m below soffit  & Temperature \\
 & TC\_A10\_2  & 0.34~m below soffit  & Temperature \\

@@

 & TC\_A10\_4  & 0.88~m below soffit  & Temperature \\
 & TC\_A10\_5  & 1.15~m below soffit  & Temperature \\
 & TC\_A10\_6  & 1.42~m below soffit  & Temperature \\
 & TC\_A10\_7  & 1.68~m below soffit  & Temperature \\
 & TC\_A10\_8  & 1.95~m below soffit  & Temperature \\

@@

 & BDP\_A10\_1 & 0.08~m below soffit  & Velocity \\
 & BDP\_A10\_2 & 0.34~m below soffit  & Velocity \\

@@

 & BDP\_A10\_4 & 0.88~m below soffit  & Velocity \\
 & BDP\_A10\_5 & 1.15~m below soffit  & Velocity \\
 & BDP\_A10\_6 & 1.42~m below soffit  & Velocity \\
 & BDP\_A10\_7 & 1.68~m below soffit  & Velocity \\
 & BDP\_A10\_8 & 1.95~m below soffit  & Velocity \\

@@

 & TC\_A11\_1  & 0.08~m below soffit  & Temperature \\
 & TC\_A11\_2  & 0.34~m below soffit  & Temperature \\

@@

 & TC\_A11\_4  & 0.88~m below soffit  & Temperature \\
 & TC\_A11\_5  & 1.15~m below soffit  & Temperature \\
 & TC\_A11\_6  & 1.42~m below soffit  & Temperature \\
 & TC\_A11\_7  & 1.68~m below soffit  & Temperature \\
 & TC\_A11\_8  & 1.95~m below soffit  & Temperature \\

@@

 & BDP\_A11\_1 & 0.08~m below soffit  & Velocity \\
 & BDP\_A11\_2 & 0.34~m below soffit  & Velocity \\

@@

 & BDP\_A11\_4 & 0.88~m below soffit  & Velocity \\
 & BDP\_A11\_5 & 1.15~m below soffit  & Velocity \\
 & BDP\_A11\_6 & 1.42~m below soffit  & Velocity \\
 & BDP\_A11\_7 & 1.68~m below soffit  & Velocity \\
 & BDP\_A11\_8 & 1.95~m below soffit  & Velocity \\

@@

 & TC\_A13\_1  & 0.08~m below soffit  & Temperature \\
 & TC\_A13\_2  & 0.34~m below soffit  & Temperature \\

@@

 & TC\_A13\_4  & 0.88~m below soffit  & Temperature \\
 & TC\_A13\_5  & 1.15~m below soffit  & Temperature \\
 & TC\_A13\_6  & 1.42~m below soffit  & Temperature \\
 & TC\_A13\_7  & 1.68~m below soffit  & Temperature \\
 & TC\_A13\_8  & 1.95~m below soffit  & Temperature \\

@@

 & BDP\_A13\_1 & 0.08~m below soffit  & Velocity \\
 & BDP\_A13\_2 & 0.34~m below soffit  & Velocity \\

@@

 & BDP\_A13\_4 & 0.88~m below soffit  & Velocity \\
 & BDP\_A13\_5 & 1.15~m below soffit  & Velocity \\
 & BDP\_A13\_6 & 1.42~m below soffit  & Velocity \\
 & BDP\_A13\_7 & 1.68~m below soffit  & Velocity \\
 & BDP\_A13\_8 & 1.95~m below soffit  & Velocity \\

@@

 & TC\_A14\_1  & 0.08~m below soffit  & Temperature \\
 & TC\_A14\_2  & 0.34~m below soffit  & Temperature \\

@@

 & TC\_A14\_4  & 0.88~m below soffit  & Temperature \\
 & TC\_A14\_5  & 1.15~m below soffit  & Temperature \\
 & TC\_A14\_6  & 1.42~m below soffit  & Temperature \\
 & TC\_A14\_7  & 1.68~m below soffit  & Temperature \\
 & TC\_A14\_8  & 1.95~m below soffit  & Temperature \\

@@

 & BDP\_A14\_1 & 0.08~m below soffit  & Velocity \\
 & BDP\_A14\_2 & 0.34~m below soffit  & Velocity \\

@@

 & BDP\_A14\_4 & 0.88~m below soffit  & Velocity \\
 & BDP\_A14\_5 & 1.15~m below soffit  & Velocity \\
 & BDP\_A14\_6 & 1.42~m below soffit  & Velocity \\
 & BDP\_A14\_7 & 1.68~m below soffit  & Velocity \\
 & BDP\_A14\_8 & 1.95~m below soffit  & Velocity \\

@@

 & HF\_2\_H	  & \begin{tabular}{@{}l} 1~m above floor, \\ facing doorway (horizontal) \end{tabular} & Total heat flux \\
 & HF\_2\_V   & \begin{tabular}{@{}l} 1~m above floor, \\ facing ceiling (vertical) \end{tabular} 	   & Total heat flux \\

@@

 & HF\_1\_H	  & \begin{tabular}{@{}l} 1~m above floor, \\ facing doorway (horizontal) \end{tabular} & Total heat flux \\
 & HF\_1\_V	  & \begin{tabular}{@{}l} 1~m above floor, \\ facing ceiling (vertical) \end{tabular} 	   & Total heat flux \\

@@

\section{East Structure Tests}
\label{sec:east_procedure}
Five different tests, Tests 2--6, were conducted in the East Structure. Tables~\ref{table:HRR_Tests_2-4} and \ref{table:HRR_Tests_5-6} list the heat release rates for each experiment. The time between the ignition of each gas burner for Tests~2--4 was on the order of minutes, while the time between the ignition of each gas burner for Tests~5 and 6 was on the order of seconds. Thus, for Tests~2--4, heat release rates are reported for each time period between a burner being turned on or off, and a single heat release rate for when all burners were ignited is reported for Tests~5 and 6.

\subsection{Tests 2--4}
Tests~2--4 followed an identical order of events. Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for each test. A 61~cm (24~in) diameter PPV fan located 1.6~m (5.2~ft) away from the south exterior door was aimed at the center of the doorway and used during Tests~2--4. During these experiments, the south exterior door was not able to completely close due to an obstruction caused by the hoses used to transport propane to the burners. So, when the south door was in the ``closed'' position, a 133~mm (5.25~in) opening was present between the door and its frame. For all other experiments, however, the south exterior door was not used and the doorway remained closed for the entirety of the test. To fully close the doorway during these tests, the hinged door was removed and gypsum board was used to cover the doorway.

\begin{table}[!ht]
\caption{Heat Release Rates for Tests~2--4}
\begin{tabular}{lccccc}
 \toprule
 					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
\textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
 \midrule
Test 2 				& 340 & 650	& 900 & 630 & 330 \\
Test 3 				& 330 & 650	& 910 & 630 & 330 \\
Test 4				& 350 & 650	& 950 & 650 & 340 \\
\bottomrule
\end{tabular}
\label{table:HRR_Tests_2-4}
\end{table}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (s) for Tests~2--4 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 	& \textbf{Test 2} & \textbf{Test 3} & \textbf{Test 4} \\
	\midrule
	~(1)~ Corner burner on 				& 	0		  	  &	 	0			&		0		  \\
	~(2)~ Middle burner on 				&   180			  &		180			&		180		  \\
	~(3)~ Center burner on 				&   360			  &	   	360			&	   	360		  \\
	~(4)~ West double door opened 		&   420			  &    	420			&	   	420		  \\
	~(5)~ East double door opened 		&   540			  &    	540			&	   	540		  \\
	~(6)~ South exterior door opened 	&   600			  &    	600			&	   	600		  \\
	~(7)~ Center burner off				&   720			  &    	780			&	   	780		  \\
	~(8)~ Middle burner off				&   840			  &    	900			&	   	900		  \\
	~(9)~ Corner burner off				&   960			  &    	1020		&	   	1020	  \\
	(10) PPV fan on 					& 	1260		  &    	1320		&  	   	1320	  \\	
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_4}
\end{minipage}
\caption{Tests~2-4 layout and event times.}
\label{fig:Tests_2-4_layout}
\end{figure}
\clearpage
